\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{color}
\usepackage{textcomp}
\usepackage{wrapfig}
\usepackage{palatino}
\usepackage[top=3.5cm, bottom=3.5cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage{fancyhdr}

\begin{document}
\title{\textit{Light} project\\Release notes}
\author{\textsc{SegFault}}
\maketitle
\section*{Alpha}
\subsection*{V0.1}
\begin{itemize}
\item First release.
\end{itemize}
\subsection*{V0.2}
\begin{itemize}
\item Bug in the background dots fixed.
\end{itemize}
\subsection*{V0.3}
\begin{itemize}
\item New cells added:
\begin{itemize}
\item Two types of cell: when one type is enabled, you can pass and see through, the other being disabled and acting like a wall.
\item Cell switcher: enable the disabled type of cell, and vice versa.
\end{itemize}
\end{itemize}
\subsection*{V0.4}
\begin{itemize}
\item New cells added:
\begin{itemize}
\item Blue portals: when you pass through a blue portal, you are teleported to the nearest one, cancelling your horizontal speed, and inverting your vertical speed.
\item Red portals: when you pass through a red portal, you are teleported to the nearest one, cancelling your horizontal speed, and conserving your vertical speed.
\end{itemize}
\item Sound effects added, which can be turned off in the options menu.
\item Big optimization concerning maps initialization.
\end{itemize}
\subsection*{V0.5}
\begin{itemize}
\item Transitions between portals have been smoothed.
\item Graphical optimizations :
\begin{itemize}
\item New textures for portals, jump pads, gravity pads and next level cells.
\end{itemize}
\item Timer added for each level, welcome speedrunners:
\begin{itemize}
\item Scores are displayed after each level name.
\item If a score is beaten, it will be deleted and replaced by the new one.
\item Scores can be deleted in the options menu. Some of my scores are already present.
\end{itemize}
\end{itemize}
\subsection*{V0.6}
\begin{itemize}
\item New cell added:
\begin{itemize}
\item Laser: a beam that kills you if it touches you.
\end{itemize}
\end{itemize}
\subsection*{V0.7}
\begin{itemize}
\item Tutorial is out. This is the first playable demo. Hope you'll enjoy it!
\end{itemize}
\end{document}